---
title       : Predicting Miles per gallon (MPG) by horsepower and weight
subtitle    : A pitch for the shiny application 
author      : Zhenhao Li

framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
url:
  lib: ../../librariesNew
  assets: ../../assets
widgets     : [mathjax]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}

---
```{r setup, cache = FALSE, echo = FALSE, message = FALSE, warning = FALSE, tidy = FALSE}
# make this an external chunk that can be included in any file
options(width = 100)
opts_chunk$set(message = F, error = F, warning = F, comment = NA, fig.align = 'center', dpi = 100, tidy = F, cache.path = '.cache/', fig.path = 'fig/')

options(xtable.type = 'html')
knit_hooks$set(inline = function(x) {
  if(is.numeric(x)) {
    round(x, getOption('digits'))
  } else {
    paste(as.character(x), collapse = ', ')
  }
})
knit_hooks$set(plot = knitr:::hook_plot_html)
```
## Two use cases
* Case 1
  * Bob knows that his car is of 200 horsepower and weighs 3000 lb
  * Bob does not know his the miles per gallon (MPG) of his car
  * Bob can use this app to get a predicted value of the MPG of his car

* Case 2
  * Alice wants to buy a new car but the dealer only knows the car's weight and horsepower
  * Alice needs to find out the MPG of that car before making her decision
  * Alice can use this app to get a predicted value of the MPG of her wanted car


---

## Prediction method

*  The app use a linear regression model to make prediction which has the form 
$$
PMG = \beta_0 + \beta_1 \text{Horsepower} + \beta_2 \text{Weight} + \epsilon
$$


* The model is built from the data set mtcars and the details of the model is shown below
```{r, echo=TRUE}
fit <- lm(mpg ~  hp  + wt, data = mtcars)
summary(fit)$coefficient
```

---

## App manule

* Use the slider Gross Horsepower to select the horsepower value 
* Use the slider Weight to select the weight value
* The predicted value of MPG will be given as a number
* The predicted value will be shown as aline in the Histogram of MPG values in mtcars if it is in the range


---

## Example Bob's car
Suppose Bob uses the app and sets the horsepower value to 200 and the weight value to 3000 lb, he would get a predicted value shown below
```{r, echo = TRUE, fig.height=5,fig.width=5}
data(mtcars)
newData <-  data.frame(hp=200, wt=3000/1000)
predict(fit, newData )
```


